Language Skills in an Ethnically Segmented Labour market: Estonia 1989 -- 2012

### 2018-07-10 paper/ijm.tex
Added a comment and two new references to bib-file.

The effect of language fluency on unemployment is shown on
Figure~\ref{fig:long-run_unemployment}, and on wage on
Figure~\ref{fig:long-run_wage}.
\fxnote{ot: SKB, I think I asked if you can slightly offset the black
  and red lines and you could not?}
The results reveal a few interesting facts.  First, the effects are
relatively stable over time, indicating that neither economic
environment nor the data quality have changed rapidly.  Estonian
fluency has been associated with less unemployment for both Russian men and
women since around year 2000, in 1990s it had little effect.  Russian fluency,
in contrast, had never had an impact on Estonians' unemployment probability.

>>>>

The effect of language fluency on unemployment is shown on
Figure~\ref{fig:long-run_unemployment}, and on wage on
Figure~\ref{fig:long-run_wage}.
\fxnote{ot: SKB, I think I asked if you can slightly offset the black
  and red lines and you could not?}
\fxnote{SKB: I do not remember such request. The only request, that I remember, is to make the scaling of the figures equal or cut off parts of the large confidence intervals, so that the scaling of the y-axis becomes smaller/more detailed.}
The results reveal a few interesting facts.  First, the effects are
relatively stable over time, indicating that neither economic
environment nor the data quality have changed rapidly.  Estonian
fluency has been associated with less unemployment for both Russian men and
women since around year 2000, in 1990s it had little effect.  Russian fluency,
in contrast, had never had an impact on Estonians' unemployment probability.
